---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tidyverse)
```

# CranberryGermplasmEAA

<!-- badges: start -->
<!-- badges: end -->

## Description

This repository contains information and code for replicating the analyses performed in the article below:

Article Title: Genomic patterns of local adaptation in wild cranberry (*Vaccinium macrocarpon* Ait.)  
Journal: G3: Genes, Genomes, Genetics (under review)  
Authors: Jeffrey L. Neyhart, Michael B. Kantar, Juan Zalapa, and Nicholi Vorsa  
Link to article


## Navigation

### Data

Data used in this study will be available from the GSA Figshare portal.

### Code

Scripts used to complete the analysis and generate figures outlined in the article above are available in the [Scripts subdirectory](https://github.com/neyhartj/CranberryGermplasmEAA/tree/master/Scripts).

Two scripts in this directory are used by all other scripts:

`startup.R` - loads packages, creates directory links, and loads data.  
`functions.R` - loads additional functions into the environment.


## Software/package versions

*R* version `r paste0(version$major, ".", version$minor)` was used to complete analyses in this project.


The following packages (with version information) were used to complete this project:

```{r version, warning=FALSE, message=FALSE, echo=FALSE}
# Scan the source function and all scripts for packages
packages <- list.files(path = getwd(), full.names = TRUE, pattern = ".R$", recursive = TRUE) %>% 
  str_subset(string = ., pattern = "OtherScripts|_local", negate = TRUE) %>%
  map(readLines) %>% 
  map(~str_subset(., "library\\(|require\\(")) %>% 
  unlist() %>% 
  str_subset(., "#", negate = TRUE) %>%
  str_trim() %>%
  str_extract("\\(.*\\)") %>% 
  str_remove_all("\\(|\\)") %>% 
  unique()

# get descriptions of each package; create a tibble
package_info <- installed.packages() %>% 
  as_tibble() %>% 
  filter(Package %in% packages) %>% 
  select(package = Package, version = Version) %>%
  arrange(package)

# Output a table
knitr::kable(package_info)
```
